# Before you go

One of the worst things to happen to a team investigating an outbreak is for a teammate to come down with an illness during the investigation.
In the best case, everyone on the team has been vaccinated against the likely infections known for the region in which the outbreak occurs.
Similarly, you may need to take prophylaxis for different pathogens before, during, and after your visit.
It may also be good to have some common drugs in case a member of the team comes down with an illness.
The best way to prepare for this is to visit a travel medicine clinic.

## Travel medicine clinic

[Travel medicine clinics](https://wwwnc.cdc.gov/travel/page/find-clinic) are typically staffed by infectious disease physicians who can recommend different vaccines, prophylaxis, and counseling on what to do in case of emergencies.
Visits to a travel medicine provider are typically covered by your insurance.

These providers will examine things like the Centers for Disease Control and Prevention (CDC)'s yellow book.
Based on the ongoing disease dynamics within the country, your will see three different categories for vaccination:

- Recommended
- Generally not recommended
- Not recommended

We can look at the [CDC recommendations for Peru](https://wwwnc.cdc.gov/travel/destinations/traveler/none/peru).

```{r}
#| echo: false
#| label: getPeruCdc
library(kableExtra)
library(rvest)
uri <- "https://wwwnc.cdc.gov/travel/destinations/traveler/none/peru"
ses <- session(uri)
tab1 <- rvest::html_table(ses)
```

::: {.content-hidden when-format="pdf"}
```{r tabCdcPeruVax}
#| echo: false
#| label: tab-tabCdcPeruVax1

tab1[[1]] |>
  gt::gt(caption = sprintf("Recommended vaccines for travelers to Peru retrieved from %s on %s", uri, Sys.Date()))
```
:::

::: {.content-visible when-format="pdf"}
```{r tabCdcPeruVax}
#| echo: false
#| label: tab-tabCdcPeruVax2


tab1[[1]] |>
  dplyr::mutate(Recommendations = stringr::str_wrap(Recommendations, 120)) |>
  kbl(format = "latex", caption = sprintf("Recommended vaccines for travelers to Peru retrieved from %s on %s", uri, Sys.Date()), booktabs = TRUE)

```
:::